Marginalization of photometric redshift uncertainties

### 2020-07-07 Paper/paper.tex
latest plots
Updates from Overleaf

      We can now write a likelihood for $\hat{\bf c}$ in which we explicitly marginalize out all the degrees of freedom associated with $\vN$:
      \begin{equation}
        \mathcal{L} \propto  \int \exp\left [-\frac{1}{2} ({\bf c}-\vt)^T C^{-1} ({\bf c}-\vt) -\frac{1}{2} (\vN - \bar{\vN})^T P^{-1} (\vN -\bar{\vN}) \right]  d^N\vN, \label{eq:like2}
      \end{equation}
      Note that in the equation above, $\vt=\vt({\bf q},\vN)$. It is the non-linear dependence of $\vt$ on $\vN$ that prevents us from performing what looks like a trivial integral analytically. In principle, we could solve this problem by making every single element of vector $\vN$ a part of an MCMC chain for ${\bf q}$ and additional hundreds of $\vN$ parameters \todo{Maybe mention HMC methods that could actually do this}. Instead, we pull an Eastern-European trick and Taylor expand theory around $\bar{\vN}$ \todo{we could change this sentence or leave it as is. But I think Taylor was British.}:
      \begin{equation}
        \vt({\bf q},\vN) \simeq \vt({\bf q},\bar{\vN}) + {\sf T} \left(\vN - \bar{\vN} \right), \label{eq:taylor}
      \end{equation}
      where the matrix ${\sf T}$ is the gradient of ${\bf t}$ with respect to $\vN$
      \begin{equation}
        {\sf T}\equiv \left.\frac{d{\bf t}}{d\vN}\right|_{{\bf q},\bar{\vN}}
      \end{equation}
      In other words it contains a full information about how all the correlation functions or power spectra respond to a small change in $N(z)$.

@@

      \subsubsection{$N(z)$ uncertainties}\label{sssec:theory.prior.cv}
        \begin{figure}[ht]
          \centering  
          \includegraphics[width=1.\textwidth]{./corr_CV_0.png}
          \caption{Correlation matrix associated to the cosmic-variance contribution to the total $N(z)$ covariance for the first tomographic bin of the HSC data. \todo{Can we make these plots pdfs instead?}}\label{fig:CV}
        \end{figure}
        The analysis presented in Section \todo{add ref} will make use of a measured redshift distribution estimated from the COSMOS 30-band catalog \todo{add ref}, as was done in \todo{add cite}. The main sources of uncertainty for this measurement are cosmic variance in the COSMOS field, shot noise and additional uncertainty in the photometric redshifts used to assign galaxies to different bins. Here we will associate each of this sources to a separate covariance that will be added in quadrature to form the final ${\sf C}_N$.

@@

\begin{figure}[ht]
\centering  
\includegraphics[width=1.2\textwidth]{./Tmat.png}
\caption{Visualization of the derivative matrix $T_{mn} = {\partial t_m}/{\partial N_n}$. \todo{Make look nicer: split into tomo bins}} 
\label{fig:Tmat}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.2\textwidth]{./Nzs.png}
\caption{Photometric redshift
distributions $N(z)$
of the four tomographic HSC bins.
The \textit{red} curves show the
default values used in the 
full HSC analysis (CITE Andrina),
while the \textit{blue} curves 
show their smoothed and upsampled 
version used in this work. The
\textit{green} show a random 
Gaussian draw from the smoothing 
prior described in Section TODO: Section}
\label{fig:Nzs}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.2\textwidth]{./Cls.png}
\caption{Galaxy power spectrum, $C_\ell^{gg}$, between the four
tomographic bins. The \textit{black} curves show the HSC-measured
power spectrum and error bars, while the
\textit{red} curves present the $C_\ell$s
computed using the posterior mean values of the 6 HOD parameters from the
full HSC analysis (CITE Andrina). In 
\textit{green} is shown the power
spectrum obtained by using the smoothed
$N(z)$ distributions (see Fig. \ref{fig:Nzs}). The \textit{blue}
curves correspond to the exact
calculation of the $C_\ell$s using the
perturbed $N(z)$ values in
Fig. \ref{fig:Nzs}, and the 
\textit{lightblue} dotted lines
show the power spectra derived via
Taylor expansion: $C_\ell' = C_\ell +
 {\sf T} \left(\vN' - {\vN} \right)$.
TODO: put in a table
Chi2 original model, original cov: 98.97
Chi2 original model, new cov  89.12
m1, m1p =  13.05 0.79
Chi2 original model, smoothed Nz, original cov: 91.33
Chi2 original model, smoothed Nz, new cov  86.25
Chi2 perturbed model smooth, original cov: 106.11
Chi2 perturbed model smooth Nz, new cov  88.37
Chi2 taylor model smooth nz, original cov: 93.48
Chi2 taylor model smooth , new cov  86.04
Ratio of determinants of original precision to CV+noise+smooth precision per dof =  1.145}
\label{fig:Cls}
\end{figure}

\begin{itemize}
  \item Plot showing $T$
  \item Plot showing exact $C_\ell$ vs linear prediction. \todo{Make your plots into subplots; verify the Tmatrix}
\end{itemize}{}
\subsection{Impact of N(z) uncertainties on final parameters}

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{./corr_data.png}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{./corr_diff.png}
  \label{fig:sub2}
\end{subfigure}
\caption{Correlation matrix for the fiducial HSC dataset (\textit{left}) and difference with its marginalized version (\textit{right}).}
\label{fig:fid_marg_cov}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./triangle_fid_marg.png}
\caption{Triangle plot with constraints of the 6 HOD parameters obtained using the covariance matrix from the full HSC dataset (\textit{red}) and from its marginalized version (\textit{blue}).}
\label{fig:triangle_fid_marg}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./triangle_marg_tests.png}
\caption{Triangle plot with constraints of the 6 HOD parameters obtained using different choices for the marginalized covariance matrix: in \textit{green} is shown the result where the diagonal noise is set to a very large value ($A_{\rm noise} = 42$); in \textit{gray} is shown the case where the marginalization is performed assuming fiducial HOD-model values which are $1\sigma$ away from their posterior mean values taken from \todo{CITE Andrina's paper}; in \textit{red} is shown the case where the smoothing has been removed ($A_{\rm smooth} = 0$); and finally in \textit{blue} is shown the fiducial case with $A_{\rm noise} = 4$ and $A_{\rm smooth} = 0.25$.}
\label{fig:triangle_marg_tests}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./importance_noburn.png}
\caption{Same as Fig.
\ref{fig:triangle_fid_marg} except 
here we apply importance sampling 
to the full 14-parameter chain 
imposing Gaussian priors on the
shift parameters with variances
[0.008,0.006,0.006,0.007] and the
width parameters with
variances [0.05,0.045,0.04,0.03],
derived by estimating their
distribution due to 
cosmic variance.}
\label{fig:triangle_fid_marg}
\end{figure}

Plots showing the effects of different things:
\begin{itemize}
\item Compare different choices of prior (smoothness, no smoothing, different degrees of noise etc.)
\item Triangle plot with T matrix computed from a different fiducial.
\item Compare CV-only covariance vs. no covariance.
\item Compare old marginalization vs. new one (maybe same plot).
\item Compare old marginalization with CV priors (importance sample).
\end{itemize}

Other results:
\begin{itemize}
  \item smoothness does nothing
  \item quote $\chi^2$ values \todo{Make a table}
\end{itemize}

\begin{center}
 \begin{tabular}{c | c c c} 
 \hline\hline
 Parameter & HSC covariance, full & HSC covariance, HOD & Marginalized covariance, HOD \\ [0.5ex] 
 \hline
 $\chi^2/\nu$ & 87.49/80 & 94.97/88 & 91.06/88 \\

 $\mu_{{\rm min},p}$ & -0.52 & -1.47 & -1.42 \\

 $\mu_{\rm min}$ & 11.88 & 11.73 & 11.73 \\

 $\mu_{0,p}$ & 1.68 & 4.86 & 5.03 \\

 $\mu_{0}$ & 0.02 & 11.53 & 11.41 \\

 $\mu_{1,p}$ & 0.87 & -0.58 & -0.51 \\

 $\mu_{1}$ & 13.073 & 12.866 & 12.873 \\ [1ex] 
 \hline
 \hline
\end{tabular}
\end{center}
%[-1.42408101 11.73454764  5.0302023  11.41301207 -0.50980494 12.87323354]
%[-1.47048791 11.73097558  4.85774675 11.52813388 -0.58053445 12.86613972]
%[ 2.18173486e-02 -1.39414027e-02 -4.61928378e-03  1.27879857e-02
% -5.18739083e-01  1.18844059e+01  1.67767553e+00  2.01822301e-02
%  8.65219859e-01  1.30726966e+01 -1.64307267e-01 -3.19342441e-02
%  3.97310971e-02  3.88321407e-02]

>>>>

      We can now write a likelihood for $\hat{\bf c}$ in which we explicitly marginalize out all the degrees of freedom associated with $\vN$:
      \begin{equation}
        \mathcal{L} \propto  \int \exp\left [-\frac{1}{2} ({\bf c}-\vt)^T C^{-1} ({\bf c}-\vt) -\frac{1}{2} (\vN - \bar{\vN})^T P^{-1} (\vN -\bar{\vN}) \right]  d^N\vN, \label{eq:like2}
      \end{equation}
      Note that in the equation above, $\vt=\vt({\bf q},\vN)$. It is the non-linear dependence of $\vt$ on $\vN$ that prevents us from performing what looks like a trivial integral analytically. In principle, we could solve this problem by making every single element of vector $\vN$ a part of an MCMC chain for ${\bf q}$ and additional hundreds of $\vN$ parameters \todo{Maybe mention HMC methods that could actually do this}. Instead, we pull an Eastern-European trick and Taylor expand theory around $\bar{\vN}$ \todo{we could change this sentence or leave it as is. But I think Taylor was British.}:
      \begin{equation}
        \vt({\bf q},\vN) \simeq \vt({\bf q},\bar{\vN}) + {\sf T} \left(\vN - \bar{\vN} \right), \label{eq:taylor}
      \end{equation}
      where the matrix ${\sf T}$ is the gradient of ${\bf t}$ with respect to $\vN$
      \begin{equation}
        {\sf T}\equiv \left.\frac{d{\bf t}}{d\vN}\right|_{{\bf q},\bar{\vN}}
        \label{eq:Tmat}
      \end{equation}
      In other words it contains a full information about how all the correlation functions or power spectra respond to a small change in $N(z)$.

@@

      \subsubsection{$N(z)$ uncertainties}\label{sssec:theory.prior.cv}
        \begin{figure}[ht]
          \centering  
          \includegraphics[width=1.\textwidth]{./corr_CV_0}
          \caption{Correlation matrix associated with the cosmic-variance contribution to the total $N(z)$ covariance for the first tomographic bin of the HSC data.}\label{fig:CV}
        \end{figure}
        The analysis presented in Section \todo{add ref} will make use of a measured redshift distribution estimated from the COSMOS 30-band catalog \todo{add ref}, as was done in \todo{add cite}. The main sources of uncertainty for this measurement are cosmic variance in the COSMOS field, shot noise and additional uncertainty in the photometric redshifts used to assign galaxies to different bins. Here we will associate each of this sources to a separate covariance that will be added in quadrature to form the final ${\sf C}_N$.

@@

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Tmat}
\caption{Visualization of the derivative matrix $T_{mn} = {\partial t_m}/{\partial N_n}$. \todo{Make look nicer: split into tomo bins}} 
\label{fig:Tmat}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Nzs}
\caption{Photometric redshift
distributions $N(z)$
of the four tomographic HSC bins.
The \textit{red} curves show the
default values used in the 
full HSC analysis (CITE Andrina),
while the \textit{blue} curves 
show their smoothed and upsampled 
version used in this work. The
\textit{green} show a random 
Gaussian draw from the smoothing 
prior described in Section TODO: Section}
\label{fig:Nzs}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Cls}
\caption{Galaxy power spectrum, $C_\ell^{gg}$, between the four
tomographic bins. The \textit{black} curves show the HSC-measured
power spectrum and error bars, while the
\textit{red} curves present the $C_\ell$s
computed using the posterior mean values of the 6 HOD parameters from the
full HSC analysis (CITE Andrina). In 
\textit{green} is shown the power
spectrum obtained by using the smoothed
$N(z)$ distributions (see Fig. \ref{fig:Nzs}). The \textit{blue}
curves correspond to the exact
calculation of the $C_\ell$s using the
perturbed $N(z)$ values in
Fig. \ref{fig:Nzs}, and the 
\textit{lightblue} dotted lines
show the power spectra derived via
Taylor expansion: $C_\ell' = C_\ell +
 {\sf T} \left(\vN' - {\vN} \right)$.}
\label{fig:Cls}
\end{figure}

\begin{table}
\begin{center}
 \begin{tabular}{c | c c } 
 \hline\hline
 Model & HSC cov. & Marginalized $N(z)$ cov. \\ [0.5ex] 
 \hline
  $\chi^2$, original $N(z)$, evaluated at $C_\ell$ & 98.97 & 88.97 \\

 $\chi^2$, smoothed $N(z)$, evaluated at $C_\ell$ & 91.33 & 86.44 \\

 $\chi^2$, perturbed $N(z)$, evaluated at $C_\ell'$ & 99.78 & 89.57 \\

 $\chi^2$, perturbed $N(z)$, taylor-expanded $C_\ell +
 {\sf T} \Delta \vN$ & 100.62 & 89.64 \\

 \hline
 \hline
\end{tabular}
\end{center}
\label{tab:lin}
\caption{$\chi^2$ values with respect to the HSC data of the four curves shown in Fig. \ref{fig:Cls}. $[\mu_1, \ \mu_{1,p}] =  [13.05, 0.79]$
Ratio of determinants of original precision to CV+noise+smooth precision per dof =  1.15
94}
\end{table}

Fig. \ref{fig:Nzs} shows the distribution of the
photometric redshifts of the HSC data

Fig. \ref{fig:Cls} displays the exact $C_\ell$ vs. 
linear prediction using the derivative matrix, ${\sf T}$.

In Fig. \ref{fig:Tmat}, we show the
derivative matrix, ${\sf T}$,
defined in Eq. \ref{eq:Tmat} for the first tomographic
bin in the HSC data and its cross-correlations with
all four bins, i.e. . The rows of the matrix correspond
to the $\ell$ multipoles, while the columns to the
redshift samples of $N(z)^1$.

\subsection{Impact of N(z) uncertainties on final parameters}
To study the effect on the covariance matrix
of the marginalization procedure described in detail
in sections TODO: CITE, we visualize the original
correlation matrix and its difference with the
marginalized matrix in Fig. \ref{fig:fid_marg_cov}. The
main effects on the original matrix is
a positive contribution to the off-diagonal entries
for redshift samples in close proximity. We set the free
parameters of our model to the following values: 
$A_{\rm smooth} = 1$, $A_{\rm noise} = 4.$,
$N_{\rm upsample} = 3$, and $\Delta z_{\rm thresh} = 
0.06$. These values were chosen so as to reduce the
$\chi^2$ of the perturbed model 
using the new covariance matrix when compared with the
original covariance matrix. The modest value of the
smoothing parameter, $A_{\rm smooth}$, ensure that we 
are not oversmoothing the $N(z)$ distribution, while
the choice of photometric noise as four times 
larger than the variance in the different photometric
measures provides a reasonable guess for the expected
variation in $N(z)$ given the uncertainty.

To assess whether the marginalization procedure 
proposed in this work provides better constraints
on the
6 HOD parameters than the original 14-parameter
model, we employ the ensemble sampler for Markov
chain Monte Carlo (MCMC) $\textsc{emcee}$ CITE Goodman 
\& Weare (2010) and other paper with 6 parameters and
a walkers' ratio of 6 for 12000 iterations. We assess
the convergence of the chains with a simple G-R test
having computed the auto-correlation and thinned the
chains beforehand. In all cases, we find that the
chains are reasonably well converged.

In Fig. \ref{fig:fid_marg_cov}, we show the key 
comparison between

We can
see that the full analysis leads to 
worse constraints on the parameters
when compared with the marginalized
covariance. Furthermore, the proximity
of the \textit{blue} and \textit{red} 
contours serves both as a sanity check 
that our method yields physical constraints
of the 6 parameters (i.e. not exceeding
the cosmic variance limits) as well as 
nearly optimal such

We, furthermore, run the following several 
tests to check the robustness of our result:
\begin{itemize}
\item We study the effect of the smoothing
by turning it off, $A_{\rm smooth} = 0$. 
\item We vary the choice for the
diagonal photometric noise parameter
by increasing it to $A_{\rm noise} = 42$.
\item We compute the ${\sf T}$ matrix 
using a different set of 
HOD parameters perturbed by $1\sigma$
away from the fiducial ones.
\end{itemize}
We show these comparisons with the
fiducial marginalized $N(z)$ model in Fig.
\ref{fig:triangle_marg_tests}.
One can notice that the effect of the
smoothing on the constraints is minimal,
while increasing the diagonal noise
leads to weakening them. Neither of these
tests changes significantly the
mean of the posterior distribution.
On the other hand, offsetting the 
HOD parameters used in the ${\sf T}$
matrix computation leads to a shift to
the mean and a slight widening of the
contours. That is because the covariance
matrix used in the analysis no longer
favors the HOD values preferred by the
data. This slight tension
results in sub-par convergence
of the chains and shifted mean posteriors.

\ref{fig:triangle_fid_marg}
\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{./corr_data}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{./corr_diff}
\end{subfigure}
\caption{Correlation matrix of the original HSC dataset (\textit{left} panel) and difference between the
original and the marginalized (this work)
correlation matrices (\textit{right} panel). Most of the
effect of marginalizing for the shift and width
parameters is manifested as a positive contribution
to the original matrix near the diagonal (i.e. there
is an increase in correlation for close redshift
values). Note that we have subtracted the diagonal
off the two matrices.}
\label{fig:fid_marg_cov}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./triangle_fid_marg}
\caption{Triangle plot with constraints of 
the 6 HOD parameters obtained using the 
covariance matrix from the full
14-parameter original HSC analysis 
(\textit{gray contours}). The \textit{red
contours} are obtained by applying
importance sampling to the full original 
chain with weights determined by the
cosmic variance constraints of the
shift and width parameters. In \textit{blue},
we show the constraints on the 6 HOD parameters
obtained using the covariance
matrix marginalized to account for the
$N(z)$ uncertainty (i.e. without the
8 shift and width parameters). We can
see that the full analysis leads to 
worse constraints on the parameters
when compared with the marginalized
covariance.}
\label{fig:triangle_fid_marg}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./triangle_marg_tests}
\caption{Triangle plot with constraints of the 6 HOD parameters obtained using different choices for the marginalized covariance matrix: in \textit{green}, we show the result where the diagonal noise is set to a very large value ($A_{\rm noise} = 42$); in \textit{gray} is shown the case where the marginalization is performed assuming fiducial HOD-model values which are $1\sigma$ away from their posterior mean values taken from \todo{CITE Andrina's paper}; in \textit{red}, we display the case where the smoothing has been removed ($A_{\rm smooth} = 0$); and finally the \textit{blue} contours show the fiducial case with $A_{\rm noise} = 4$ and $A_{\rm smooth} = 1$.}
\label{fig:triangle_marg_tests}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{c | c c c c} 
 \hline\hline
 Parameter & HSC cov. [68\%, 95\%] & CV constraints [68\%, 95\%] & Marg. $N(z)$ [68\%, 95\%] \\ [0.5ex] 
 \hline
 $\chi^2/\nu$ & 87.49/80 & --- & 88.54/88 \\ 
$\mu_{{\rm min},p}$ & $-0.5^{+1.7}_{-2.0}$, $^{+4.0}_{-4.0}$ & $-0.4^{+1.1}_{-1.4}$, $^{+2.5}_{-2.3}$ & $-0.3^{+1.5}_{-1.8}$, $^{+3.2}_{-2.8}$ \\ [1ex]
$\mu_{\rm min}$ & $11.90^{+0.26}_{-0.15}$, $^{+0.39}_{-0.46}$ & $11.86^{+0.19}_{-0.16}$, $^{+0.28}_{-0.30}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.32}_{-0.36}$ \\ [1ex]
$\mu_{0,p}$ & $2.4\pm 4.3$, $^{+7.2}_{-7.0}$ & $2.1^{+4.2}_{-5.1}$, $^{+6.6}_{-7.2}$ & $2.7^{+6.7}_{-4.4}$, $^{+6.9}_{-7.1}$ \\ [1ex]
$\mu_{0}$ & $5.7\pm 3.3$, $^{+5.5}_{-5.5}$ & $6.1^{+4.6}_{-3.8}$, $^{+5.2}_{-4.8}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ \\ [1ex]
$\mu_{1,p}$ & $0.9^{+2.0}_{-2.8}$, $^{+5.1}_{-4.7}$ & $0.9^{+1.3}_{-1.8}$, $^{+3.4}_{-2.9}$ & $1.0^{+1.6}_{-2.6}$, $^{+4.1}_{-3.5}$ \\ [1ex]
$\mu_{1}$ & $13.10^{+0.30}_{-0.21}$, $^{+0.48}_{-0.54}$ & $13.04\pm 0.21$, $^{+0.38}_{-0.40}$ & $13.00^{+0.25}_{-0.21}$, $^{+0.42}_{-0.44}$ \\ [1ex]
 \hline
 \hline
\end{tabular}
\end{center}
\label{tab:chi2_tests}
\caption{Table showing the minimum
$\chi^2$ value as well as the 68\% and 95\% constraints on the 6 HOD parameters
in three regimes: using the original
HSC covariance matrix with 14 parameters (6 HOD + 8 $N(z)$ ones),
importance-sampling the original
chain to get cosmic variance constraints on the parameters, and finally using the
marginalized $N(z)$ covariance matrix with the 6 HOD parameters developed in this work.}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{c | c c c c} 
 \hline\hline
 Parameter & Fiducial [68\%, 95\%] & Test 1 [68\%, 95\%] & Test 2 [68\%, 95\%] & Test 3 [68\%, 95\%] \\ [0.5ex] 
 \hline
 $\chi^2/\nu$ & 88.54/88 & 87.67/88 & 88.56/88 & 78.61/88 \\ 
$\mu_{{\rm min},p}$ & $-0.3^{+1.5}_{-1.8}$, $^{+3.2}_{-2.8}$ & $0.0\pm 1.7$, $^{+3.2}_{-3.3}$ & $-0.3^{+1.4}_{-1.8}$, $^{+3.2}_{-2.8}$ & $-0.8^{+1.8}_{-2.1}$, $^{+3.7}_{-3.5}$ \\ [1ex]
$\mu_{\rm min}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.32}_{-0.36}$ & $11.85^{+0.22}_{-0.13}$, $^{+0.31}_{-0.37}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.33}_{-0.36}$ & $11.76^{+0.26}_{-0.17}$, $^{+0.38}_{-0.43}$ \\ [1ex]
$\mu_{0,p}$ & $2.7^{+6.7}_{-4.4}$, $^{+6.9}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ \\ [1ex]
$\mu_{0}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ & $5.8^{+3.6}_{-5.2}$, $^{+5.6}_{-5.5}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ & $5.9\pm 3.4$, $^{+5.5}_{-5.6}$ \\ [1ex]
$\mu_{1,p}$ & $1.0^{+1.6}_{-2.6}$, $^{+4.1}_{-3.5}$ & $1.5^{+2.1}_{-2.6}$, $^{+4.3}_{-3.9}$ & $0.98^{+1.5}_{-2.5}$, $^{+4.2}_{-3.5}$ & $0.6^{+1.9}_{-2.9}$, $^{+4.6}_{-4.0}$ \\ [1ex]
$\mu_{1}$ & $13.00^{+0.25}_{-0.21}$, $^{+0.42}_{-0.44}$ & $13.03^{+0.26}_{-0.20}$, $^{+0.41}_{-0.45}$ & $13.00^{+0.25}_{-0.22}$, $^{+0.42}_{-0.44}$ & $12.93^{+0.29}_{-0.24}$, $^{+0.47}_{-0.50}$ \\ [1ex]
 \hline
 \hline
\end{tabular}
\end{center}
\label{tab:chi2_tests}
\caption{Table}
\end{table}
